Tables

### 2023-11-07 output/paper/figures.qmd
Modified pipeline so that targets for processing results do not actually produce eg plots but only ready to use tibbles for plots and tables. Tested pipeline to create paper but I think I still have to manually reference tables and figures in manuscript.

@@

>>>>

```{r}
source("code/proc_res.R")
```

```{r vars}
store <- ifelse(
  Sys.getenv("is_hpc"), 
  paste0(
    "/PROJECTES/HELIX_OMICS/DATA_PREVIOUS_MIGRATION/",
    "lorenzoF/data/data_paper3/_targets/_targets_res"
  ), 
  "~/mounts/rstudioserver/data/data_paper3/_targets/_targets_res"
)

num_digits_est = 3
num_digits_sig = 2
```

@@

## Marginal comparisons

```{r}
targets::tar_load(
  dplyr::matches("marginal_comparisons_(\\d)$"),
  store = store
)
```

```{r marginal-1}
#| label: fig-marginal-1
#| fig-cap: Average comparisons
#| fig-width: 6
#| fig-height: 7

tidy_res_meffects(
  df = marginal_comparisons_1,
  sa_var = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```

```{r marginal-2}
#| label: fig-marginal-2
#| fig-cap: Average comparisons
#| fig-width: 10
#| fig-height: 10

tidy_res_meffects(
  df = marginal_comparisons_2,
  sa_var = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```

```{r marginal-3}
#| label: fig-marginal-3
#| fig-cap: Average comparisons
#| fig-width: 5
#| fig-height: 5

tidy_res_meffects(
  df = marginal_comparisons_3,
  sa_var = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```

### 2023-11-07 output/paper/si.qmd
Modified pipeline so that targets for processing results do not actually produce eg plots but only ready to use tibbles for plots and tables. Tested pipeline to create paper but I think I still have to manually reference tables and figures in manuscript.

@@

@@

@@

>>>>

crossref:
  fig-title: Supplementary Figure
  tbl-title: Supplementary Table

@@

## Directed Acyclic Graphs

```{r dag-1}
targets::tar_load("all_dags", store = store)
cat(all_dags$chem_to_out)
```

```{r dag-2}
cat(all_dags$chem_to_marker)
```

```{r dag-3}
cat(all_dags$marker_to_out)
```

@@

```{r codebook-1}
#| label: tbl-codebook-1
#| tbl-cap: Codebook for covariates used in RQ1

targets::tar_load(
  dplyr::contains("codebook_"),
  store = store
)
codebook_1
```

```{r codebook-2}
#| label: tbl-codebook-2
#| tbl-cap: Codebook for covariates used in RQ2

codebook_2
```

```{r codebook-3}
#| label: tbl-codebook-3
#| tbl-cap: Codebook for covariates used in RQ3

codebook_3
```

## Other results

### Balancing weights for effect modification

```{r}
targets::tar_load(
  dplyr::matches("weights_(\\d)SA$"),
  store = store
)
```

```{r weights-1sa}
#| label: tbl-weights-1sa
#| tbl-cap: Weights

tidy_res_weighted_fits(
  dat_tbl = weights_1SA$dat_tbl,
  dat_plt = weights_1SA$dat_plt,
  sa_var = "e3_sex"
)$table
```

```{r weights-2sa}
#| label: tbl-weights-2sa
#| tbl-cap: Weights

tidy_res_weighted_fits(
  dat_tbl = weights_2SA$dat_tbl,
  dat_plt = weights_2SA$dat_plt,
  sa_var = "e3_sex"
)$table
```

```{r weights-3sa}
#| label: tbl-weights-3sa
#| tbl-cap: Weights

tidy_res_weighted_fits(
  dat_tbl = weights_3SA$dat_tbl,
  dat_plt = weights_3SA$dat_plt,
  sa_var = "e3_sex"
)$table
```

@@

## Other results

### Marginal comparisons for effect modification

```{r}
targets::tar_load(
  dplyr::matches("marginal_comparisons_(\\d)SA$"),
  store = store
)
```

```{r marginal-1sa}
#| label: fig-marginal-1sa
#| fig-cap: Average comparisons for effect modification
#| fig-width: 6
#| fig-height: 7

tidy_res_meffects(
  df = marginal_comparisons_1SA,
  sa_var = "e3_sex",
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```

```{r marginal-2sa}
#| label: fig-marginal-2sa
#| fig-cap: Average comparisons for effect modification
#| fig-width: 10
#| fig-height: 10

tidy_res_meffects(
  df = marginal_comparisons_2SA,
  sa_var = "e3_sex",
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```

```{r marginal-3sa}
#| label: fig-marginal-3sa
#| fig-cap: Average comparisons for effect modification
#| fig-width: 5
#| fig-height: 5

tidy_res_meffects(
  df = marginal_comparisons_3SA,
  sa_var = "e3_sex",
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```

### 2023-11-07 output/paper/tables.qmd
Modified pipeline so that targets for processing results do not actually produce eg plots but only ready to use tibbles for plots and tables. Tested pipeline to create paper but I think I still have to manually reference tables and figures in manuscript.

@@

```{r}
#| label: tbl-chem-info
#| tbl-cap: "Information about the non-persistent EDCs."

edcs_info <- myphd::edcs_information() |>
  tidylog::select(-c(chem_id, smiles))
gt::gt(edcs_info,
       groupname_col = "class") |>
  gt::cols_label(
    full_name = "Compound",
    short_name = "Symbol",
    pubchem_cid = "PubChem CID",
    ctd_id = "CTD ID",
    exposome_explorer_id = "Exposome Explore ID",
    parental_compound = "Parental compound"
  ) |>
  gt::tab_style(
    locations = gt::cells_column_labels(columns = everything()),
    style = list(
      gt::cell_borders(sides = "bottom", weight = gt::px(3)),
      gt::cell_text(weight = "bold")
    )
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  )
```

@@

@@

- RQ2: group chemicals by class, and for each chemical report results with metabolites (`avg_comparisons` with estimate, SE, s-value, CI).
- RQ3: report results with outcome (`avg_comparisons` with estimate, SE, s-value, CI).

@@

>>>>

```{r pop-desc}
#| label: tbl-pop-desc
#| tbl-cap: Population description

targets::tar_load("table1", store = store)
table1
```

@@

```{r edc-desc}
#| label: tbl-edc-desc
#| tbl-cap: Levels of unprocessed chemicals

targets::tar_load("desc_chems_mets", store = store)
desc_chems_mets$desc_chems
```

@@

```{r met-desc}
#| label: tbl-met-desc
#| tbl-cap: Levels of unprocessed corticosteroids

desc_chems_mets$desc_mets
```

@@

## Balancing weights

```{r}
targets::tar_load(
  dplyr::matches("weights_(\\d)$"),
  store = store
)
```

```{r weights-1}
#| label: tbl-weights-1
#| tbl-cap: Weights

tidy_res_weighted_fits(
  dat_tbl = weights_1$dat_tbl,
  dat_plt = weights_1$dat_plt,
  sa_var = NULL
)$table
```

```{r weights-2}
#| label: tbl-weights-2
#| tbl-cap: Weights

tidy_res_weighted_fits(
  dat_tbl = weights_2$dat_tbl,
  dat_plt = weights_2$dat_plt,
  sa_var = NULL
)$table
```

```{r weights-3}
#| label: tbl-weights-3
#| tbl-cap: Weights

tidy_res_weighted_fits(
  dat_tbl = weights_3$dat_tbl,
  dat_plt = weights_3$dat_plt,
  sa_var = NULL
)$table
```

## Marginal comparisons

```{r}
targets::tar_load(
  dplyr::matches("marginal_comparisons_(\\d)$"),
  store = store
)
```

```{r marginal-1}
#| label: tbl-marginal-1
#| tbl-cap: Average comparisons

tidy_res_meffects(
  df = marginal_comparisons_1,
  sa_var = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```

```{r marginal-2}
#| label: tbl-marginal-2
#| tbl-cap: Average comparisons

tidy_res_meffects(
  df = marginal_comparisons_2,
  sa_var = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```

```{r marginal-3}
#| label: tbl-marginal-3
#| tbl-cap: Average comparisons

tidy_res_meffects(
  df = marginal_comparisons_3,
  sa_var = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```

@@

## Marginal hypothesis

```{r}
targets::tar_load(
  dplyr::matches("marginal_hypothesis_(\\d)SA$"),
  store = store
)
```

```{r hypothesis-1}
#| label: tbl-hypothesis-1
#| tbl-cap: Hypothesis testing for effect modification

tidy_res_meffects(
  df = marginal_hypothesis_1SA,
  sa_var = "e3sex",
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```

```{r hypothesis-2}
#| label: tbl-hypothesis-2
#| tbl-cap: Hypothesis testing for effect modification

tidy_res_meffects(
  df = marginal_hypothesis_2SA,
  sa_var = "e3sex",
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```

```{r hypothesis-3}
#| label: tbl-hypothesis-3
#| tbl-cap: Hypothesis testing for effect modification

tidy_res_meffects(
  df = marginal_hypothesis_3SA,
  sa_var = "e3sex",
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```
